Universal regime transition for water resources utilization in developing river basins

### 2020-10-03 tex/main/manuscript.tex
update discussion 2

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.85\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the changing relationship between watershed development and water resources.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization. Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis. (1) Stress of water utilization shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies. (3) configuration can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different. When abrupt transitions occur during this process, they may indicate a regime shift in water utilization, so we need an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

\section*{Results}
\subsection*{Water utilization regimes}
% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048 and -0.09 in change contributions, 5.6\% and 10.7\% in net contributions, respectively).
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636 change contribution and 50.2\% net contribution). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and configuration (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is configuration.

@@

% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts of water utilization, as transition phases in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a universal transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution. 
% 水资源压力
(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency. Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a “natural cycle” (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards dualistic water cycle. In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural phases, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal, for identify regime shifts of water utilization.

\subsection*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it may help to predict possible dilemmas in development.

>>>>

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the changing relationship between watershed development and water resources.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (stress, priority and configuration) of water resources utilization. Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources utilization changes along that axis. (1) Stress of water utilization shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) Priority of water utilization can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies. (3) configuration can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water utilization regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the development of society, their combined water resource utilization status is also different. When abrupt transitions occur during this process, they may indicate a regime shift in water utilization, so we need an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

\section*{Results}
\subsection*{Water utilization regimes}

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}

% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking contribution (+0.722 change contribution and 83.7\% net contribution), while priority and configuration of the water utilization had slight negative contribution (-0.048 and -0.09 in change contributions, 5.6\% and 10.7\% in net contributions, respectively).
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, despite positive contributions of priority and configuration of water utilization (+0.352 and +0.279 in change contributions, 22.0\% and 27.8\% in net contributions respectively), because of increasing stresses on water resource playing a larger negative role (-0.636 change contribution and 50.2\% net contribution). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization priority (+0.485 change contribution and 36.1\% net contribution) and configuration (+0.515 and 38.3\%, corresponding), and decelerations of water stresses (-0.344 change contribution, 46\% less than P2) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress; P2 is priority; and P3 is configuration.

@@

% 上述过渡过程与稳态转换的关联可能是普遍的
The association between the above transition process and the regime shifts may be pervasive.
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water utilization, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts of water utilization, with changing in three related dimensions induced by social development, are of the most important characteristics towards natural-social dualistic cycle
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a universal transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:summary}).

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the transition towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of changes. 
% 水资源压力
(1) Firstly, although stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles in different aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural cycle'' (Figure~\ref{fig:summary}A) to one in local or regional cycle (Figure~\ref{fig:summary} B and C), towards a natural-society dualistic water cycle. In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal in interpreting regime shifts of water utilization.

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it may help to predict possible dilemmas in development.
